---
title: "fisheR sample usage"
author: "Nick Young & Quinn Asena"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
fig_caption: yes
bibliography: library.bib
biblio-style: apalike
link-citations: yes  
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Package info
This package for calculating Fisher's information follows methods from @cabezas_san_2010, @eason_evaluating_2012, and @ahmad_using_2016. Python code from @ahmad_using_2016 and MATLAB code from @cabezas_san_2010 has been adapted for modelling in R. For reproducibility purposes we use the 'sample_data' provided by @ahmad_using_2016 as an example which is the GDP per capita and total population of the USA from 1960 to 2013. For detailed descriptions on how to conduct Fisher's information see @cabezas_san_2010, @eason_evaluating_2012 and @ahmad_using_2016, we recommend reading these references first if unfamiliar with Fisher's Information.

## Example run
The `fisher` function takes a dataframe as an input and an optional size of state (`sos`) dataframe. If a size of state dataframe is not provided one will be created following methods from @cabezas_san_2010, @eason_evaluating_2012 and @ahmad_using_2016.

The `fisher` function calculates: 1) the size of state; 2) Fisher's Information; and 3) Fisher's Information smoothed with a block mean of the desired window size. The final output is a dataframe where the last three columns are the Fisher's Information means, Fisher's Information smoothed and time-windows.

**NOTE:**

  * Data structure for input dataframe must have the first column as time-steps and following columns containing the variables of interest
  
  * NA values will be replaced by 0
  
  * Take care with the `header` argument if reading in a csv

  

```{r, fig.show='hold', fig.cap = "Fisher's Information calculated from the Sample Data"}
library(fisheR)
df = read.csv("../sample_data.csv", header=F)
sos = sost(df)
df_FI = fisher(df, sos = sos)
```


> "To consult the statistician after an experiment is finished is often merely to ask him to conduct _a post mortem_ examination. He can
 perhaps say what the experiment"
  - R. A. Fisher [@fisher_presidential_1938]
